\myTitle

### 2024-07-08 002-GSI_and_Fst.Rmd
Re-ran all notebooks.  Some editing.

```{r}
if(exists("snakemake")) {
  input_list <- snakemake@input
  output_list <- snakemake@output
} else {
  input_list <- list(
    final_baseline = "data/subRoSA_baseline_rubias_loci_renamed_July_2024.csv.gz",
    final_baseline_apr = "data/subRoSA_baseline_rubias_APR2024_w_mixture_revised_rosa_added.csv",
    lfar_genos = "data/metagenos_hap2col_lfar_all_samps.csv",
    pop_labels = "inputs/reference-collection-names.csv",
    map_notations = "inputs/map-notations.tsv"
  )
  # outputs:
  output_list <- list(
    assig_table = "results/GSI_and_Fst/assignment-table-full-baseline.pdf",
    fst_table = "results/GSI_and_Fst/full-baseline-but-no-lfar-Fst-table.pdf",
    assig_table_lfar_all = "results/GSI_and_Fst/assignment-table-full-baseline-plus-lfar.pdf",
    ass_table80 = "results/GSI_and_Fst/ass-table-80.pdf",
    rosa_gsi_table = "results/GSI_and_Fst/rosa-gsi-table.pdf",
    tex_table = "tex/inputs/samples-table.tex",
    gsi_fst_fig = "results/GSI_and_Fst/gsi_and_fst_fig.pdf",
    gsi_fst_fig_crop = "results/GSI_and_Fst/gsi_and_fst_fig-crop.pdf",
    gsi_fst_fig_tex = "tex/images/gsi_and_fst_fig-crop.pdf",
    ass_table80_crop = "results/GSI_and_Fst/ass-table-80-crop.pdf",
    ass_table80_tex = "tex/images/ass-table-80-crop.pdf",
    rosa_gsi_table_crop = "results/GSI_and_Fst/rosa-gsi-table-crop.pdf",
    rosa_gsi_table_tex = "tex/images/rosa-gsi-table-crop.pdf",
    pop_gen_by_loc_coll = "tex/supp_data/Supp-Data-2-pop-gen-summaries-by-locus-and-collection.csv"
  )
}

@@

lfar_genos <- read_csv(input_list$lfar_genos)

@@

# long format with no missing data
long_genos <- full_base2 %>%
select(-repunit, -sample_type) %>%
pivot_longer(
cols = -c(indiv, collection),
names_to = c("locus", "gene_copy"),
values_to = "allele",
names_pattern = "(.*)[_.]([12])$"
) %>%
filter(!is.na(allele))

>>>>

```{r}
if(exists("snakemake")) {
  input_list <- snakemake@input
  output_list <- snakemake@output
} else {
  input_list <- list(
    final_baseline = "data/SWFSC-chinook-reference-baseline.csv.gz",
    pop_labels = "inputs/reference-collection-names.csv",
    map_notations = "inputs/map-notations.tsv"
  )
  # outputs:
  output_list <- list(
    assig_table = "results/GSI_and_Fst/assignment-table-full-baseline.pdf",
    fst_table = "results/GSI_and_Fst/full-baseline-but-no-lfar-Fst-table.pdf",
    assig_table_lfar_all = "results/GSI_and_Fst/assignment-table-full-baseline-plus-lfar.pdf",
    ass_table80 = "results/GSI_and_Fst/ass-table-80.pdf",
    rosa_gsi_table = "results/GSI_and_Fst/rosa-gsi-table.pdf",
    tex_table = "tex/inputs/samples-table.tex",
    gsi_fst_fig = "results/GSI_and_Fst/gsi_and_fst_fig.pdf",
    gsi_fst_fig_crop = "results/GSI_and_Fst/gsi_and_fst_fig-crop.pdf",
    gsi_fst_fig_tex = "tex/images/gsi_and_fst_fig-crop.pdf",
    ass_table80_crop = "results/GSI_and_Fst/ass-table-80-crop.pdf",
    ass_table80_tex = "tex/images/ass-table-80-crop.pdf",
    rosa_gsi_table_crop = "results/GSI_and_Fst/rosa-gsi-table-crop.pdf",
    rosa_gsi_table_tex = "tex/images/rosa-gsi-table-crop.pdf",
    pop_gen_by_loc_coll = "tex/supp_data/Supp-Data-2-pop-gen-summaries-by-locus-and-collection.csv"
  )
}

@@

@@

# long format with no missing data.  We filter out NA locus to get rid of the rosa_geno_str which
# we are not using
long_genos <- full_base2 %>%
  select(-repunit, -sample_type) %>%
  pivot_longer(
    cols = -c(indiv, collection),
    names_to = c("locus", "gene_copy"),
    values_to = "allele",
    names_pattern = "(.*)[_]([12])$"
  ) %>%
  filter(!is.na(allele) & !is.na(locus))

### 2024-07-08 003-ckmr-sim-evaluation.Rmd
Re-ran all notebooks.  Some editing.

```{r}
if(exists("snakemake")) {
  input_list <- snakemake@input
  output_list <- snakemake@output
} else {
  input_list <- list(
    final_baseline = "data/subRoSA_baseline_rubias_loci_renamed_July_2024.csv.gz",
    pop_labels = "inputs/reference-collection-names.csv",
    locus_info = "inputs/Calif-Chinook-Amplicon-Panel-Information.csv"
  )
  output_list <- list(
    ckmr_figure = "results/ckmr-sim-eval/fpr-fnr-figure.pdf",
    ckmr_figure_crop = "results/ckmr-sim-eval/fpr-fnr-figure-crop.pdf",
    ckmr_figure_tex = "tex/images/fpr-fnr-figure-crop.pdf",
    ckmr_comp = "results/ckmr-sim-eval/cmkr-comp-figure.pdf",
    ckmr_comp_crop = "results/ckmr-sim-eval/cmkr-comp-figure-crop.pdf",
    ckmr_comp_tex = "tex/images/cmkr-comp-figure-crop.pdf"

>>>>

```{r}
if(exists("snakemake")) {
  input_list <- snakemake@input
  output_list <- snakemake@output
} else {
  input_list <- list(
    final_baseline = "data/SWFSC-chinook-reference-baseline.csv.gz",
    pop_labels = "inputs/reference-collection-names.csv",
    locus_info = "inputs/Calif-Chinook-Amplicon-Panel-Information.csv"
  )
  output_list <- list(
    ckmr_figure = "results/ckmr-sim-eval/fpr-fnr-figure.pdf",
    ckmr_figure_crop = "results/ckmr-sim-eval/fpr-fnr-figure-crop.pdf",
    ckmr_figure_tex = "tex/images/fpr-fnr-figure-crop.pdf",
    ckmr_comp = "results/ckmr-sim-eval/cmkr-comp-figure.pdf",
    ckmr_comp_crop = "results/ckmr-sim-eval/cmkr-comp-figure-crop.pdf",
    ckmr_comp_tex = "tex/images/cmkr-comp-figure-crop.pdf"

### 2024-07-08 004-lfar-allele-freqs.Rmd
Re-ran all notebooks.  Some editing.

```{r}
if(exists("snakemake")) {
  input_list <- snakemake@input
  output_list <- snakemake@output
} else {
  # inputs:
  input_list <- list(
    final_baseline = "data/subRoSA_baseline_rubias_loci_renamed_July_2024.csv.gz",
    pop_labels = "inputs/reference-collection-names.csv",
    locus_info = "inputs/Calif-Chinook-Amplicon-Panel-Information.csv"
  )
  # outputs:
  output_list <- list(
    lfar_tex_table = "tex/inputs/lfar-freqs.tex"
  )
}
# you can create the necessary output directories like this:
dump <- lapply(output_list, function(x)
  dir.create(dirname(x), recursive = TRUE, showWarnings = FALSE)
)
```

>>>>

```{r}
if(exists("snakemake")) {
  input_list <- snakemake@input
  output_list <- snakemake@output
} else {
  # inputs:
  input_list <- list(
    final_baseline = "data/SWFSC-chinook-reference-baseline.csv.gz",
    pop_labels = "inputs/reference-collection-names.csv",
    locus_info = "inputs/Calif-Chinook-Amplicon-Panel-Information.csv"
  )
  # outputs:
  output_list <- list(
    lfar_tex_table = "tex/inputs/lfar-freqs.tex"
  )
}
# you can create the necessary output directories like this:
dump <- lapply(output_list, function(x)
  dir.create(dirname(x), recursive = TRUE, showWarnings = FALSE)
)
```

### 2024-07-08 005-plotting-genome-locations-of-markers.Rmd
Re-ran all notebooks.  Some editing.

Now, we get the markers on there
```{r}
amplicons2 <- amplicons %>%
  filter(!str_detect(Otsh_v2.0_chromosome, "NW")) %>%
  mutate(
    chrom_y = 35 - as.numeric(Otsh_v2.0_chromosome),
    mb = AmpliconStartPos / 1e6,
    Type = factor(Type, levels = c("SNPtype", "Microhap", "RoSA", "LFAR", "WRAP", "VGLL3", "Six6"))
  )

@@

>>>>

Now, we get the markers on there
```{r}
amplicons2 <- amplicons %>%
  filter(!str_detect(Otsh_v2.0_chromosome, "NW")) %>%
  mutate(
    chrom_y = 35 - as.numeric(Otsh_v2.0_chromosome),
    mb = AmpliconStartPos / 1e6,
    Type = factor(Type, levels = c("SNPtype", "Microhap", "RoSA", "LFAR", "WRAP", "VGLL3", "Six6", "Coho"))
  )

@@

# Citations

::: {#refs}
:::

# Session Info

```{r}
sessioninfo::session_info()
```

# Running Time

Running the code and rendering this notebook required approximately this much time:

```{r}
Sys.time() - start_time
```

### 2024-07-08 tex/body-text-of-paper.tex
Re-ran all notebooks.  Some editing.

\subsubsection*{Identifying and Designing markers from the Late-Fall Associated Region}

@@

Leave-one-out cross-validation (self-assignment) analysis demonstrates that this
reference baseline provides a high degree of accuracy for distinguishing the major
groups of Chinook salmon in California.  The results of the analysis are summarized
in a self-assignment matrix (Figure~\ref{fig:gsi}). 
%%%%%%%%%%%%%%%%%%%%%% 
\begin{figure}
\newcommand{\gsicap}{\footnotesize Pairwise $F_\mathrm{ST}$ values and allele frequencies({\bf a)} 
and self-assignment rates
 ({\bf b)}  for the collections in the baseline.  The codes of the populations
appear on the outer margins of the table atop cells colored according to the run-timing group
of the collection.  Interior cells in which the column and row correspond to the same reporting
unit are colored according to the reporting unit.  In ({\bf a}), for $F_\mathrm{ST}$ values, the upper triangle was computed using the baseline microhaplotype
data. Each cell in the lower triangle shows a small scatter plot of estimated allele frequencies
in the collections---the $x$ value is allele frequencies from the collection in the column and the
$y$ value is from the collection in the row. Frequencies for all alleles are shown, with values within
each cell ranging from 0 to 1.  These frequencies were estimated by, for each locus, randomly
subsampling individuals from each collection to the minimum number of observed alleles in any collection
at the locus.  In ({\bf b}), for self-assignment tallies, the row corresponds
to the true source collection and the column corresponds to the assigned collection.
\comment{Hey! Didn't we drop one of the LFARs? I see three, still.}}
\begin{center}
\includegraphics[width=\columnwidth]{images/gsi_and_fst_fig-crop.pdf}
\end{center}
\caption[\gsicap]{\gsicap}
\label{fig:gsi}
\end{figure}
%%%%%%%%%%%%%%%%%%%%
This figure shows the collections divided into seven different reporting groups:
SO-Ncal-Coast,  Klamath-Trinity, Cent. Cal. Coast,
CV-Winter, CV-Spring, CV-Fall, and  CV-Late-Fall.  \comment{Really, where and how
do we want to introduce these reporting units?} These groupings correspond
largely to the divisions in the data found by STRUCTURE, and they also correspond
with divisions amongst the stocks as defined for management.

>>>>

\subsubsection*{Identifying the Late-Fall Associated Region and designing markers therein}

@@

Leave-one-out cross-validation (self-assignment) analysis demonstrates that this
reference baseline provides a high degree of accuracy for distinguishing the major
groups of Chinook salmon in California.  The results of the analysis are summarized
in a self-assignment matrix (Figure~\ref{fig:gsi}). 
%%%%%%%%%%%%%%%%%%%%%% 
\begin{figure}
\newcommand{\gsicap}{\footnotesize Pairwise $F_\mathrm{ST}$ values and allele frequencies({\bf a)} 
and self-assignment rates
 ({\bf b)}  for the collections in the baseline.  The codes of the populations
appear on the outer margins of the table atop cells colored according to the run-timing group
of the collection.  Interior cells in which the column and row correspond to the same reporting
unit are colored according to the reporting unit.  In ({\bf a}), for $F_\mathrm{ST}$ values, the upper triangle was computed using the baseline microhaplotype
data. Each cell in the lower triangle shows a small scatter plot of estimated allele frequencies
in the collections---the $x$ value is allele frequencies from the collection in the column and the
$y$ value is from the collection in the row. Frequencies for all alleles are shown, with values within
each cell ranging from 0 to 1.  These frequencies were estimated by, for each locus, randomly
subsampling individuals from each collection to the minimum number of observed alleles in any collection
at the locus.  In ({\bf b}), for self-assignment tallies, the row corresponds
to the true source collection and the column corresponds to the assigned collection.}
\begin{center}
\includegraphics[width=\columnwidth]{images/gsi_and_fst_fig-crop.pdf}
\end{center}
\caption[\gsicap]{\gsicap}
\label{fig:gsi}
\end{figure}
%%%%%%%%%%%%%%%%%%%%
This figure shows the collections divided into seven different reporting groups:
SO-Ncal-Coast,  Klamath-Trinity, Cent. Cal. Coast,
CV-Winter, CV-Spring, CV-Fall, and  CV-Late-Fall.  \comment{Really, where and how
do we want to introduce these reporting units?} These groupings correspond
largely to the divisions in the data found by STRUCTURE, and they also correspond
with divisions amongst the stocks as defined for management.

### 2024-07-08 tex/supplemental-figures.tex
Re-ran all notebooks.  Some editing.

%%%%%%%%%%%%%%%%%%%%%% 
\begin{figure}
\begin{center}
\includegraphics[width=0.7\textwidth]{images/num-alle-barplot.pdf}
\end{center}
\caption[Number of loci with different
total numbers of alleles]{\footnotesize Number of loci with different
total numbers of alleles in the data set.}
\label{fig:num-alle}
\end{figure}
%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%% 
\begin{figure}
\begin{center}
\includegraphics[width=0.7\textwidth]{images/num-alle-barplot.pdf}
\end{center}
\caption[Number of loci with different
total numbers of alleles]{\footnotesize Number of loci with different
total numbers of alleles in the data set. The one amplicon with only
one allele is {\tt Ots\_coho001\_05\_32691399}, which is fixed for alternate
in Chinook vs.\ coho salmon. It is helpful in identifying coho samples that are
misidentified during sampling as Chinook salmon.}
\label{fig:num-alle}
\end{figure}
%%%%%%%%%%%%%%%%%%%%
